### 2011-11-01 paper.tex
SCFGs

where $U,V,X,Y \in (\nodelabels \cup \terminals^\ast)$
and $B,C \in (\nodelabels \cup \{\epsilon\}^\ast)$.
The tree is ordered left-to-right.

@@

>>>>

where $U,V,X,Y \in (\nodelabels \cup \terminals^\ast)$
and $B,C \in (\nodelabels \cup \{\epsilon\}^\ast)$.
(The tree is ordered left-to-right.)
Parsing this general form using a bottom-up, CYK approach would take ${\cal O}(|\outseq|^{10})$ time.
If the rules are restricted to the types shown in \tabref{RuleTypes},
CYK parsing becomes ${\cal O}(|\outseq|^6)$ in time.

@@

\subsubsection{Context-free grammars as a subset of TAGs}

We can further restrict the rules of \tabref{RuleTypes} to recover the basic repertoire of a context-free grammar.
For example, bifurcation rules ($A \to U\ C$)
may be interpreted as type-1 rules from \tabref{RuleTypes} (with $v=x=y=\epsilon$),
while emission rules ($A \to u\ C\ y$)
may be interpreted as type-6 rules (with $v=x=\epsilon$),

\subsubsection{Derivation weights}
